GVN-Hoist: Hoisting Computations from Branches

### 2016-08-12 hoist.tex
future work

\section{Cost models}
Similar to any compiler optimization pass, there are several cost functions that
are deployed to tune for optimal combination of performance and code-size.
Since this is mostly a code-size optimization pass, the goal is to not regress
in performance across popular benchmarks at the same time reduce code size as
much as possible. Following are the cost models which are implemented:

@@

\subsubsection{Exposing more ILP}
Code hoisting can also reduce the critical path length of execution in out of
order machines. As more instructios are available at the hoisting point, the
hardware has more instructions to reorder. Following example illustrates how
hoisting can improve performance by exposing more ILP.

@@

\section{Conclusion and Future Work}
\label{sec:future-work}

>>>>

\section{Cost models}
\label{sec:cost-models}
Similar to any compiler optimization pass, there are several cost functions that
are deployed to tune for optimal combination of performance and code-size.
Since this is mostly a code-size optimization pass, the goal is to not regress
in performance across popular benchmarks at the same time reduce code size as
much as possible. Following are the cost models which are implemented:

@@

\subsection{Exposing more ILP}
Code hoisting can also reduce the critical path length of execution in out of
order machines. As more instructios are available at the hoisting point, the
hardware has more instructions to reorder. Following example illustrates how
hoisting can improve performance by exposing more ILP.

@@

\section{Conclusion and Future Work}
\label{sec:future-work}
We have presented the GVN based code hoisting algorithm. The primary goal is to
reduce the code size but it benefits performance in some cases as well. To
preserve performance and not hoist too much we have implemented several cost
models \ref{sec:cost-models}. Since those cost models depend on a set of thresholds,
it requires tuning, as such, we used representative benchmarks to tune them.
